---
title: "Check CI"
output: html_notebook
---


# CI_check_A1-A6.R
# Purpose : Generate the A1--A6 supplementary tables for variance, correlation, and bias
# Inputs  : all generated csvz in results including bias_results.csv 
# Outputs : Latex tables 
# Authors : Vijay Kumar
# Updated : March 2026

```{r}

library(survival)
library(ggplot2)
library(broom)
library(haven)
library(dplyr)
library(tidyr)
library(readr)
library(MASS)
library(lubridate)
library(lme4)
library(glmmTMB)
library(ggplot2)
library(knitr) # this package was added
library(kableExtra) # this package was added

options(readr.show_col_types = FALSE)  # suppress column spec messages globally
rm(list=ls())
```

Read null and association data

```{r}
truedta_null <- read_csv("/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/truedta_null_Final.csv")
truedta_ass <- read_csv("/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/truedta_ass_Final.csv")

truedta_null$term_births <- truedta_null$all_births - truedta_null$preterm_births
truedta_ass$term_births  <- truedta_ass$all_births - truedta_ass$preterm_births
```


Variance and Correlation of each scenario inside one experiment.



```{r}
# --- Paths ---
base_path <- "/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/exp/exp_049/Results/"
scenario_names <- c(
  "nondiff_null", "diff_null_moreErr", "diff_null_lessErr", "diff_null_lessErr50", "diff_null_moreErr50",
  "nondiff_harm", "diff_harm_moreErr", "diff_harm_lessErr", "diff_harm_lessErr50", "diff_harm_moreErr50"
)

# --- Error Levels ---
err.lev <- c(0, 0.5, 1, 2)

# --- True Variance ---
var_pm25 <- var(truedta_ass$pm25)

# --- Initialize results list ---
all_results <- list()

set.seed(212)  # ensures Var_Corr.csv values are reproducible

# --- Loop through each scenario ---
for (scen in scenario_names) {
  cat("\nProcessing scenario:", scen, "\n")

  # Load results
  diff_res <- read_csv(paste0(base_path, scen, ".csv"))
  cor_res  <- read_csv(paste0(base_path, "cor_", scen, ".csv"))

  # Select correct dataset based on scenario
  dta <- if (grepl("null", scen)) truedta_null else truedta_ass

  # Variance of observed exposure for error levels
  variances_pm_err <- numeric(length(err.lev))

  for (e in 1:length(err.lev)) {

    if (grepl("nondiff", scen)) {
      # Non-differential: same error for all observations
      pm.err <- rnorm(nrow(dta), dta$pm25,
                      err.lev[e] * sd(dta$pm25))
      variances_pm_err[e] <- var(pm.err)

    } else {
      # Differential: different error by risk group
      pm.err.norisk <- rnorm(nrow(dta), dta$pm25,
                             err.lev[e] * sd(dta$pm25))

      if (grepl("moreErr", scen)) {
        pm.err.hirisk <- rnorm(nrow(dta), dta$pm25,
                               (err.lev[e] * 10) * sd(dta$pm25))
      } else if (grepl("lessErr", scen)) {
        pm.err.hirisk <- rnorm(nrow(dta), dta$pm25,
                               (err.lev[e] / 10) * sd(dta$pm25))
      }

      # Weighted combination — 50% scenarios
      if (grepl("50", scen)) {
        pm.err <- ifelse(dta$all_births > 0,
                         (0.5 * dta$term_births    * pm.err.norisk +
                          0.5 * dta$term_births    * pm.err.hirisk +
                               dta$preterm_births  * pm.err.hirisk) /
                           dta$all_births,
                         mean(c(pm.err.norisk, pm.err.hirisk)))
      } else {
        pm.err <- ifelse(dta$all_births > 0,
                         (dta$term_births    * pm.err.norisk +
                          dta$preterm_births * pm.err.hirisk) /
                           dta$all_births,
                         mean(c(pm.err.norisk, pm.err.hirisk)))
      }
      variances_pm_err[e] <- var(pm.err)
    }
  }

  # Compute average correlation from saved simulation results
  correlations <- colMeans(cor_res)

  # Output variance comparison
  variance_comparison <- data.frame(
    Error_Level     = err.lev,
    Variance_pm25   = var_pm25,
    Variance_pm_err = variances_pm_err
  )
  print(variance_comparison)

  # Correlation plot
  plot(err.lev, correlations, type = "b", col = "red",
       xlab = "Error Level", ylab = "Correlation (pm.err vs pm25)",
       main = paste("Correlation vs Error Levels (", scen, ")", sep = ""))

  # Coefficients and SEs
  coef_means <- colMeans(diff_res[, grep("b_",  names(diff_res))])
  se_means   <- colMeans(diff_res[, grep("se_", names(diff_res))])

  # Plot coefficients and SEs
  par(mfrow = c(1, 2))
  plot(err.lev, coef_means, type = "b", col = "blue",
       xlab = "Error Level", ylab = "Mean Coefficient (b)",
       main = paste("Effect of Error on Coefficient (", scen, ")", sep = ""))
  plot(err.lev, se_means, type = "b", col = "green",
       xlab = "Error Level", ylab = "Mean SE",
       main = paste("Effect of Error on SE (", scen, ")", sep = ""))
  par(mfrow = c(1, 1))

  # Store results
  all_results[[scen]] <- data.frame(
    Scenario                = scen,
    Error_Level             = err.lev,
    Variance_pm25           = var_pm25,
    Variance_pm_err         = variances_pm_err,
    Correlation_pm_err_pm25 = correlations
  )

  cat("Completed scenario:", scen, "\n")
}

cat("\nAll scenarios processed!\n")

# Combine and save
final_results <- do.call(rbind, all_results)
write_csv(final_results,
          "/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/exp/exp_049/Results/Var_Corr.csv")
```

Experiment E2

```{r}
base_path <- "/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/exp/exp_050/Results/"
scenario_names <- c(
  "nondiff_null", "diff_null_moreErr", "diff_null_lessErr", "diff_null_lessErr50", "diff_null_moreErr50", 
  "nondiff_harm", "diff_harm_moreErr", "diff_harm_lessErr", "diff_harm_lessErr50", "diff_harm_moreErr50"
)

# --- Error Levels ---
err.lev <- c(0, 0.5, 1, 2)

# --- True Variance ---
var_pm25 <- var(truedta_ass$pm25)

# --- Systematic shift for E2 ---
c_shift <- 0.25  # = +2.5 ug/m3 in rescaled units

# --- Initialize results list ---
all_results <- list()
set.seed(212)  # ensures Var_Corr.csv values are reproducible

# --- Loop through each scenario ---
for (scen in scenario_names) {
  cat("\nProcessing scenario:", scen, "\n")
  
  # Load results
  diff_res <- read_csv(paste0(base_path, scen, ".csv"))
  cor_res  <- read_csv(paste0(base_path, "cor_", scen, ".csv"))
  
  # Variance of observed exposure for error levels
  variances_pm_err <- numeric(length(err.lev))
  
  for (e in 1:length(err.lev)) {
    
    if (grepl("nondiff", scen)) {
      # Non-differential: c_shift applied to ALL observations
      pm.err <- rnorm(nrow(truedta_ass), 
                      truedta_ass$pm25 + c_shift,
                      err.lev[e] * sd(truedta_ass$pm25))
      variances_pm_err[e] <- var(pm.err)
      
    } else {
      # Differential: c_shift applied to high-risk group only
      # norisk — no shift, baseline error
      pm.err.norisk <- rnorm(nrow(truedta_ass), 
                             truedta_ass$pm25,
                             err.lev[e] * sd(truedta_ass$pm25))
      
      # hirisk — c_shift in mean, error magnitude depends on scenario
      if (grepl("moreErr", scen)) {
        pm.err.hirisk <- rnorm(nrow(truedta_ass), 
                               truedta_ass$pm25 + c_shift,
                               (err.lev[e] * 10) * sd(truedta_ass$pm25))
      } else if (grepl("lessErr", scen)) {
        pm.err.hirisk <- rnorm(nrow(truedta_ass), 
                               truedta_ass$pm25 + c_shift,
                               (err.lev[e] / 10) * sd(truedta_ass$pm25))
      }
      
      # Weighted combination by birth counts
      if (grepl("50", scen)) {
        # 50% of non-risk also gets high-risk error
        pm.err <- ifelse(truedta_ass$all_births > 0,
                         (0.5 * truedta_ass$term_births * pm.err.norisk +
                          0.5 * truedta_ass$term_births * pm.err.hirisk +
                               truedta_ass$preterm_births * pm.err.hirisk) /
                           truedta_ass$all_births,
                         mean(c(pm.err.norisk, pm.err.hirisk)))
      } else {
        # Standard weighting
        pm.err <- ifelse(truedta_ass$all_births > 0,
                         (truedta_ass$term_births    * pm.err.norisk +
                          truedta_ass$preterm_births * pm.err.hirisk) /
                           truedta_ass$all_births,
                         mean(c(pm.err.norisk, pm.err.hirisk)))
      }
      variances_pm_err[e] <- var(pm.err)
    }
  }
  
  # Output variance comparison
  variance_comparison <- data.frame(
    Error_Level     = err.lev,
    Variance_pm25   = var_pm25,
    Variance_pm_err = variances_pm_err
  )
  print(variance_comparison)
  
  # Correlation plot
  correlations <- colMeans(cor_res)
  plot(err.lev, correlations, type = "b", col = "red",
       xlab = "Error Level", ylab = "Correlation (pm.err vs pm25)",
       main = paste("Correlation vs Error Levels (", scen, ")", sep = ""))
  
  # Coefficients and SEs
  coef_means <- colMeans(diff_res[, grep("b_",  names(diff_res))])
  se_means   <- colMeans(diff_res[, grep("se_", names(diff_res))])
  
  # Plot coefficients and SEs
  par(mfrow = c(1, 2))
  plot(err.lev, coef_means, type = "b", col = "blue",
       xlab = "Error Level", ylab = "Mean Coefficient (b)",
       main = paste("Effect of Error on Coefficient (", scen, ")", sep = ""))
  plot(err.lev, se_means, type = "b", col = "green",
       xlab = "Error Level", ylab = "Mean SE",
       main = paste("Effect of Error on SE (", scen, ")", sep = ""))
  par(mfrow = c(1, 1))
  
  # Store results
  all_results[[scen]] <- data.frame(
    Scenario                 = scen,
    Error_Level              = err.lev,
    Variance_pm25            = var_pm25,
    Variance_pm_err          = variances_pm_err,
    Correlation_pm_err_pm25  = correlations
  )
  
  cat("Completed scenario:", scen, "\n")
}

cat("\nAll scenarios processed!\n")

# Combine and save
final_results <- do.call(rbind, all_results)
write_csv(final_results, 
          "/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/exp/exp_050/Results/Var_Corr.csv")
```

Experiment E3

```{r}
base_path <- "/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/exp/exp_051/Results/"
scenario_names <- c(
  "nondiff_null", "diff_null_moreErr", "diff_null_lessErr", "diff_null_lessErr50", "diff_null_moreErr50", 
  "nondiff_harm", "diff_harm_moreErr", "diff_harm_lessErr", "diff_harm_lessErr50", "diff_harm_moreErr50"
)

# --- Error Levels ---
err.lev <- c(0, 0.5, 1, 2)

# --- True Variance ---
var_pm25 <- var(truedta_ass$pm25)

# --- Systematic shift for E2 ---
c_shift <- -0.25  # = +2.5 ug/m3 in rescaled units

# --- Initialize results list ---
all_results <- list()

set.seed(212)  # ensures Var_Corr.csv values are reproducible

# --- Loop through each scenario ---
for (scen in scenario_names) {
  cat("\nProcessing scenario:", scen, "\n")
  
  # Load results
  diff_res <- read_csv(paste0(base_path, scen, ".csv"))
  cor_res  <- read_csv(paste0(base_path, "cor_", scen, ".csv"))
  
  # Variance of observed exposure for error levels
  variances_pm_err <- numeric(length(err.lev))
  
  for (e in 1:length(err.lev)) {
    
    if (grepl("nondiff", scen)) {
      # Non-differential: c_shift applied to ALL observations
      pm.err <- rnorm(nrow(truedta_ass), 
                      truedta_ass$pm25 + c_shift,
                      err.lev[e] * sd(truedta_ass$pm25))
      variances_pm_err[e] <- var(pm.err)
      
    } else {
      # Differential: c_shift applied to high-risk group only
      # norisk — no shift, baseline error
      pm.err.norisk <- rnorm(nrow(truedta_ass), 
                             truedta_ass$pm25,
                             err.lev[e] * sd(truedta_ass$pm25))
      
      # hirisk — c_shift in mean, error magnitude depends on scenario
      if (grepl("moreErr", scen)) {
        pm.err.hirisk <- rnorm(nrow(truedta_ass), 
                               truedta_ass$pm25 + c_shift,
                               (err.lev[e] * 10) * sd(truedta_ass$pm25))
      } else if (grepl("lessErr", scen)) {
        pm.err.hirisk <- rnorm(nrow(truedta_ass), 
                               truedta_ass$pm25 + c_shift,
                               (err.lev[e] / 10) * sd(truedta_ass$pm25))
      }
      
      # Weighted combination by birth counts
      if (grepl("50", scen)) {
        # 50% of non-risk also gets high-risk error
        pm.err <- ifelse(truedta_ass$all_births > 0,
                         (0.5 * truedta_ass$term_births * pm.err.norisk +
                          0.5 * truedta_ass$term_births * pm.err.hirisk +
                               truedta_ass$preterm_births * pm.err.hirisk) /
                           truedta_ass$all_births,
                         mean(c(pm.err.norisk, pm.err.hirisk)))
      } else {
        # Standard weighting
        pm.err <- ifelse(truedta_ass$all_births > 0,
                         (truedta_ass$term_births    * pm.err.norisk +
                          truedta_ass$preterm_births * pm.err.hirisk) /
                           truedta_ass$all_births,
                         mean(c(pm.err.norisk, pm.err.hirisk)))
      }
      variances_pm_err[e] <- var(pm.err)
    }
  }
  
  # Output variance comparison
  variance_comparison <- data.frame(
    Error_Level     = err.lev,
    Variance_pm25   = var_pm25,
    Variance_pm_err = variances_pm_err
  )
  print(variance_comparison)
  
  # Correlation plot
  correlations <- colMeans(cor_res)
  plot(err.lev, correlations, type = "b", col = "red",
       xlab = "Error Level", ylab = "Correlation (pm.err vs pm25)",
       main = paste("Correlation vs Error Levels (", scen, ")", sep = ""))
  
  # Coefficients and SEs
  coef_means <- colMeans(diff_res[, grep("b_",  names(diff_res))])
  se_means   <- colMeans(diff_res[, grep("se_", names(diff_res))])
  
  # Plot coefficients and SEs
  par(mfrow = c(1, 2))
  plot(err.lev, coef_means, type = "b", col = "blue",
       xlab = "Error Level", ylab = "Mean Coefficient (b)",
       main = paste("Effect of Error on Coefficient (", scen, ")", sep = ""))
  plot(err.lev, se_means, type = "b", col = "green",
       xlab = "Error Level", ylab = "Mean SE",
       main = paste("Effect of Error on SE (", scen, ")", sep = ""))
  par(mfrow = c(1, 1))
  
  # Store results
  all_results[[scen]] <- data.frame(
    Scenario                 = scen,
    Error_Level              = err.lev,
    Variance_pm25            = var_pm25,
    Variance_pm_err          = variances_pm_err,
    Correlation_pm_err_pm25  = correlations
  )
  
  cat("Completed scenario:", scen, "\n")
}

cat("\nAll scenarios processed!\n")

# Combine and save
final_results <- do.call(rbind, all_results)
write_csv(final_results, 
          "/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/exp/exp_051/Results/Var_Corr.csv")
```

Finally, create tables A1-A3
```{r}
library(xtable)
library(dplyr)

# ── Function to generate formatted LaTeX table ────────────────────────────────
generate_var_corr_latex <- function(final_results, 
                                     experiment_label = "E1",
                                     caption_text = NULL,
                                     label_text = NULL) {
  
  # Default caption and label based on experiment
  if (is.null(caption_text)) {
    caption_text <- switch(experiment_label,
      "E1" = "Variance of ``true'' \\PM\\ exposure and Pearson $r_p$ correlation coefficients between ``true'' and error-prone \\PM\\ across scenarios on the \\PM\\--PTB association across experiment E1 (random error). Error scenarios are described in Section~\\ref{subsec:error_scenarios}.",
      "E2" = "Variance of ``true'' \\PM\\ exposure and Pearson $r_p$ correlation coefficients between ``true'' and error-prone \\PM\\ across scenarios on the \\PM\\--PTB association across experiment E2 (random error plus positive constant $c=+2.5$ \\mug). Error scenarios are described in Section~\\ref{subsec:error_scenarios}.",
      "E3" = "Variance of ``true'' \\PM\\ exposure and Pearson $r_p$ correlation coefficients between ``true'' and error-prone \\PM\\ across scenarios on the \\PM\\--PTB association across experiment E3 (random error plus negative constant $c=-2.5$ \\mug). Error scenarios are described in Section~\\ref{subsec:error_scenarios}."
    )
  }
  
  if (is.null(label_text)) {
    label_text <- paste0("tab:var_corr_results_", experiment_label)
  }
  
  # ── Scenario display names ─────────────────────────────────────────────────
  scenario_labels <- c(
    "nondiff_null"       = "nondiff\\_null",
    "diff_null_lessErr"  = "diff\\_null\\_lessErr",
    "diff_null_lessErr50"= "diff\\_null\\_lessErr50",
    "diff_null_moreErr"  = "diff\\_null\\_moreErr",
    "diff_null_moreErr50"= "diff\\_null\\_moreErr50",
    "nondiff_harm"       = "nondiff\\_harm",
    "diff_harm_lessErr"  = "diff\\_harm\\_lessErr",
    "diff_harm_lessErr50"= "diff\\_harm\\_lessErr50",
    "diff_harm_moreErr"  = "diff\\_harm\\_moreErr",
    "diff_harm_moreErr50"= "diff\\_harm\\_moreErr50"
  )
  
  # ── Group labels ───────────────────────────────────────────────────────────
  null_scenarios <- c("nondiff_null", "diff_null_lessErr", "diff_null_lessErr50",
                      "diff_null_moreErr", "diff_null_moreErr50")
  harm_scenarios <- c("nondiff_harm", "diff_harm_lessErr", "diff_harm_lessErr50",
                      "diff_harm_moreErr", "diff_harm_moreErr50")
  
  # ── Build LaTeX manually ───────────────────────────────────────────────────
  lines <- c(
    "\\begin{table}[ht]",
    "\\centering",
    "\\footnotesize",
    "\\setlength{\\tabcolsep}{4pt}",
    "\\begin{tabular}{llcrrr}",
    "  \\toprule",
    "Group & Scenario & Error Level & Var($X_{it}$) & Var($Z_{it}$) & $r_p(X_{it}, Z_{it})$ \\\\",
    "  \\midrule",
    "% ======= NULL group =======",
    "\\multirow{20}{*}{\\makebox[60pt][c]{\\rotatebox[origin=c]{90}{NULL}}}"
  )
  
  # NULL scenarios
  for (s in seq_along(null_scenarios)) {
    scen <- null_scenarios[s]
    scen_label <- scenario_labels[scen]
    scen_data <- final_results %>% 
      filter(Scenario == scen) %>%
      arrange(Error_Level)
    
    if (s == 1) {
      prefix <- paste0(" & \\multirow{4}{*}{", scen_label, "}")
    } else {
      prefix <- paste0("                      & \\multirow{4}{*}{", scen_label, "}")
    }
    
    for (r in 1:nrow(scen_data)) {
      row <- scen_data[r, ]
      if (r == 1) {
        lines <- c(lines, sprintf("%s\n                        & %s & %.2f & %.2f & %.2f \\\\",
                                  prefix,
                                  row$Error_Level,
                                  row$Variance_pm25,
                                  row$Variance_pm_err,
                                  row$Correlation_pm_err_pm25))
      } else {
        lines <- c(lines, sprintf("                      &  & %s & %.2f & %.2f & %.2f \\\\",
                                  row$Error_Level,
                                  row$Variance_pm25,
                                  row$Variance_pm_err,
                                  row$Correlation_pm_err_pm25))
      }
    }
    
    if (s < length(null_scenarios)) {
      lines <- c(lines, "                      \\cline{2-6}")
    }
  }
  
  lines <- c(lines,
    "  \\midrule",
    "% ======= HARM group =======",
    "\\multirow{20}{*}{\\makebox[60pt][c]{\\rotatebox[origin=c]{90}{HARMFUL}}}"
  )
  
  # HARM scenarios
  for (s in seq_along(harm_scenarios)) {
    scen <- harm_scenarios[s]
    scen_label <- scenario_labels[scen]
    scen_data <- final_results %>%
      filter(Scenario == scen) %>%
      arrange(Error_Level)
    
    if (s == 1) {
      prefix <- paste0(" & \\multirow{4}{*}{", scen_label, "}")
    } else {
      prefix <- paste0("                      & \\multirow{4}{*}{", scen_label, "}")
    }
    
    for (r in 1:nrow(scen_data)) {
      row <- scen_data[r, ]
      if (r == 1) {
        lines <- c(lines, sprintf("%s\n                        & %s & %.2f & %.2f & %.2f \\\\",
                                  prefix,
                                  row$Error_Level,
                                  row$Variance_pm25,
                                  row$Variance_pm_err,
                                  row$Correlation_pm_err_pm25))
      } else {
        lines <- c(lines, sprintf("                      &  & %s & %.2f & %.2f & %.2f \\\\",
                                  row$Error_Level,
                                  row$Variance_pm25,
                                  row$Variance_pm_err,
                                  row$Correlation_pm_err_pm25))
      }
    }
    
    if (s < length(harm_scenarios)) {
      lines <- c(lines, "                      \\cline{2-6}")
    }
  }
  
  # ── Close table ────────────────────────────────────────────────────────────
  lines <- c(lines,
    "  \\bottomrule",
    "\\end{tabular}",
    paste0("\\caption{", caption_text, "}"),
    paste0("\\label{", label_text, "}"),
    "\\footnotetext{$X_{it}$: ``true'' \\PM; $Z_{it}$: error-prone \\PM; $r_p$: Pearson correlation coefficient; nondiff\\_null: Non-differential null; diff\\_null\\_lessErr: Differential null with less error; diff\\_null\\_moreErr: Differential null with more error; diff\\_null\\_lessErr50: Differential null with less error in risk population and 50\\% of rest; diff\\_null\\_moreErr50: Differential null with more error in risk population and 50\\% of rest.}",
    "\\end{table}"
  )
  
  cat(paste(lines, collapse = "\n"))
}

# ── Generate tables for each experiment ───────────────────────────────────────

# E1
final_results_E1 <- read_csv("/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/exp/exp_049/Results/Var_Corr.csv")
set.seed(212)
generate_var_corr_latex(final_results_E1, experiment_label = "E1")

# E2
final_results_E2 <- read_csv("/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/exp/exp_050/Results/Var_Corr.csv")
set.seed(212)
generate_var_corr_latex(final_results_E2, experiment_label = "E2")

# E3
final_results_E3 <- read_csv("/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/exp/exp_051/Results/Var_Corr.csv")
set.seed(212)
generate_var_corr_latex(final_results_E3, experiment_label = "E3")
```

Table A4-A6
For tables, we need bias data from results
```{r}
generate_bias_latex <- function(bias_results_path,
                                 experiment_label = "E1",
                                 caption_text = NULL,
                                 label_text = NULL) {
  
  # Default caption and label
  if (is.null(caption_text)) {
    caption_text <- switch(experiment_label,
      "E1" = "Bias under null (RR = 1) and harmful (RR = 1.115) scenarios for experiment E1 (random error only). Values show percent bias (harmful) or absolute bias (null) with 95\\% intervals (2.5\\textsuperscript{th}--97.5\\textsuperscript{th} percentile across simulations) and percent coverage. Error scenarios are described in Section~\\ref{subsec:error_scenarios}.",
      "E2" = "Bias under null (RR = 1) and harmful (RR = 1.115) scenarios for experiment E2 (random error plus positive constant $c=+2.5$ \\mug). Values show percent bias (harmful) or absolute bias (null) with 95\\% intervals (2.5\\textsuperscript{th}--97.5\\textsuperscript{th} percentile across simulations) and percent coverage. Error scenarios are described in Section~\\ref{subsec:error_scenarios}.",
      "E3" = "Bias under null (RR = 1) and harmful (RR = 1.115) scenarios for experiment E3 (random error plus negative constant $c=-2.5$ \\mug). Values show percent bias (harmful) or absolute bias (null) with 95\\% intervals (2.5\\textsuperscript{th}--97.5\\textsuperscript{th} percentile across simulations) and percent coverage. Error scenarios are described in Section~\\ref{subsec:error_scenarios}."
    )
  }
  
  if (is.null(label_text)) {
    label_text <- paste0("tab:", experiment_label, "_CI_combined")
  }
  
  # ── Scenario order ─────────────────────────────────────────────────────────
  null_scenarios <- c("nondiff null", "diff null lessErr", "diff null lessErr50",
                      "diff null moreErr", "diff null moreErr50")
  harm_scenarios <- c("nondiff harm", "diff harm lessErr", "diff harm lessErr50",
                      "diff harm moreErr", "diff harm moreErr50")
  
  # ── Scenario display names ─────────────────────────────────────────────────
  scenario_labels <- c(
    "nondiff null"        = "nondiff\\_null",
    "diff null lessErr"   = "diff\\_null\\_lessErr",
    "diff null lessErr50" = "diff\\_null\\_lessErr50",
    "diff null moreErr"   = "diff\\_null\\_moreErr",
    "diff null moreErr50" = "diff\\_null\\_moreErr50",
    "nondiff harm"        = "nondiff\\_harm",
    "diff harm lessErr"   = "diff\\_harm\\_lessErr",
    "diff harm lessErr50" = "diff\\_harm\\_lessErr50",
    "diff harm moreErr"   = "diff\\_harm\\_moreErr",
    "diff harm moreErr50" = "diff\\_harm\\_moreErr50"
  )
  
  # ── Load and process data ──────────────────────────────────────────────────
  bias_results <- read_csv(bias_results_path, show_col_types = FALSE)
  
  table_data <- bias_results %>%
    separate(scenario,
             into = c("type", "effect", "errtype", "error_level"),
             sep = "_", fill = "right") %>%
    mutate(
      error_level = ifelse(type == "nondiff", errtype, error_level),
      errtype     = ifelse(type == "nondiff", NA, errtype)
    ) %>%
    mutate(
      Group    = ifelse(effect == "null", "NULL", "HARMFUL"),
      Scenario = ifelse(type == "nondiff",
                        paste(type, effect),
                        paste(type, effect, errtype)),
      error_level = factor(error_level, levels = c("0", "0.5", "1", "2"))
    ) %>%
    arrange(Group, Scenario, error_level)
  
  # ── Build LaTeX manually ───────────────────────────────────────────────────
  lines <- c(
    "\\begin{table}[ht]",
    paste0("\\caption{", caption_text, "}"),
    "\\centering",
    "\\footnotesize",
    "\\setlength{\\tabcolsep}{4pt}",
    "\\begin{tabular}{l l c r r r}",
    "\\toprule",
    "Group & Scenario & Error Level & Bias & 95\\% intervals & Coverage \\\\",
    "\\midrule",
    "% ======= NULL group =======",
    "\\multirow{20}{*}{\\makebox[60pt][c]{\\rotatebox[origin=c]{90}{NULL}}}"
  )
  
  # NULL scenarios
  for (s in seq_along(null_scenarios)) {
    scen      <- null_scenarios[s]
    scen_label <- scenario_labels[scen]
    scen_data  <- table_data %>% filter(Scenario == scen)
    
    prefix <- paste0(" & \\multirow{4}{*}{", scen_label, "}")
    
    for (r in 1:nrow(scen_data)) {
      row <- scen_data[r, ]
      bias_str <- sprintf("%.1f", row$bias_mean)
      ci_str   <- sprintf("(%.1f, %.1f)", row$bias_2.5, row$bias_97.5)
      cov_str  <- as.character(round(row$coverage))
      
      if (r == 1) {
        lines <- c(lines,
          sprintf("%s & %s & %s & %s & %s \\\\",
                  prefix, as.character(row$error_level),
                  bias_str, ci_str, cov_str))
      } else {
        lines <- c(lines,
          sprintf("            &  & %s & %s & %s & %s \\\\",
                  as.character(row$error_level),
                  bias_str, ci_str, cov_str))
      }
    }
    
    if (s < length(null_scenarios)) {
      lines <- c(lines, "                            \\cline{2-6}")
    }
  }
  
  lines <- c(lines,
    "\\midrule",
    "% ======= HARM group =======",
    "\\multirow{20}{*}{\\makebox[60pt][c]{\\rotatebox[origin=c]{90}{HARMFUL}}}"
  )
  
  # HARM scenarios
  for (s in seq_along(harm_scenarios)) {
    scen       <- harm_scenarios[s]
    scen_label <- scenario_labels[scen]
    scen_data  <- table_data %>% filter(Scenario == scen)
    
    prefix <- paste0(" & \\multirow{4}{*}{", scen_label, "}")
    
    for (r in 1:nrow(scen_data)) {
      row <- scen_data[r, ]
      bias_str <- sprintf("%.1f", row$bias_mean)
      ci_str   <- sprintf("(%.1f, %.1f)", row$bias_2.5, row$bias_97.5)
      cov_str  <- as.character(round(row$coverage))
      
      if (r == 1) {
        lines <- c(lines,
          sprintf("%s & %s & %s & %s & %s \\\\",
                  prefix, as.character(row$error_level),
                  bias_str, ci_str, cov_str))
      } else {
        lines <- c(lines,
          sprintf("            &  & %s & %s & %s & %s \\\\",
                  as.character(row$error_level),
                  bias_str, ci_str, cov_str))
      }
    }
    
    if (s < length(harm_scenarios)) {
      lines <- c(lines, "                                \\cline{2-6}")
    }
  }
  
  # ── Close table ────────────────────────────────────────────────────────────
  lines <- c(lines,
    "\\bottomrule",
    "\\end{tabular}",
    paste0("\\label{", label_text, "}"),
    "\\footnotetext{nondiff\\_null: Non-differential null; diff\\_null\\_lessErr: Differential null with less error; diff\\_null\\_moreErr: Differential null with more error; diff\\_null\\_lessErr50: Differential null with less error in risk population and 50\\% of rest; diff\\_null\\_moreErr50: Differential null with more error in risk population and 50\\% of rest.}",
    "\\end{table}"
  )
  
  cat(paste(lines, collapse = "\n"))
}

# ── Generate tables for each experiment ───────────────────────────────────────
generate_bias_latex(
  "/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/exp/exp_049/Results/bias_results.csv",
  experiment_label = "E1"
)

generate_bias_latex(
  "/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/exp/exp_050/Results/bias_results.csv",
  experiment_label = "E2"
)

generate_bias_latex(
  "/scratch/user/u.vk230134/Downloads/DiffMeasError/CodeReview/exp/exp_051/Results/bias_results.csv",
  experiment_label = "E3"
)
```


